
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{dirtytalk}
\usepackage{comment}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%----------HEADING----------
\begin{document}

\begin{center}
    {\Huge \scshape ASIF ENAN} \\ \vspace{1pt}
    2039 Q Street - Apt-202 Lincoln, Nebraska 68503 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 402-525-7437 ~ \href{mailto:asifenan774@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{aenan2@huskers.unl.edu}} ~ 
    \href{https://linkedin.com/in/asifenan/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/asifenan/}}  \\
    \vspace{3pt}
    Availability: Summer 2025 for Internship  % Plain text, no italics
    \vspace{-8pt}
\end{center}}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
\resumeSubheading
  {University of Dhaka}{January 2018 -- June 2023}
  {Bachelor of Science in Statistics}{Dhaka, Bangladesh}
  \vspace{-4pt}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{GPA: 3.80 / 4.00 [WES Evaluation: 3.88 / 4.00]}
  \end{itemize}
      \resumeSubheading
  {University of Nebraska-Lincoln}{August 2024 -- Present}
  {Master of Science in Statistics [Ongoing]}{Lincoln, NE, USA}
  \resumeSubHeadingListEnd
\vspace{-10pt}



%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Research Project}{January 2022 -- December 2022}
    {}{}
    {\textbf{Title}: Early Childhood Development: Variation Within Age at Marriage and Birth of Children among Women in Bangladesh}
    \vspace{-5pt}
      \resumeItemListStart
        \resumeItem{Explored ways to understand the mechanism through which a mother's age at marriage and at birth of children affects the development of children aged 3-4 years using the Bangladesh MICS 2019 data.}
        \resumeItem{Conducted Chi-Squared tests to determine the factors associated with Early Childhood Development (ECD) across three different cohorts of children.}
        \resumeItem{Fitted three binary logistic regression models to assess the factors that have a significant effect on ECD.}
        \resumeItem{Study identified factors such as the mother’s education level, age of the child, and attendance at an early childhood education program and others to be significant predictors of ECD.}
      \resumeItemListEnd   
  \resumeSubHeadingListEnd
\vspace{-13pt}


%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {University of Nebraska-Lincoln}{August 2024 -- Present}
      {Graduate Teaching Assistant}{Lincoln, NE, USA}
      \resumeItemListStart
        \resumeItem{Graded assignments, exams, and quizzes for undergraduate course in Statistics [STAT-218].}
        \resumeItem{Conducted office hours to assist students with course material, answer questions, and provide guidance on assignments.}
      \resumeItemListEnd
    \resumeSubheading
      {Luminedge Bangladesh}{February 2024 -- May 2024}
      {IELTS Teaching Assistant}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Conducted classes for groups of 10 students on developing listening, reading, writing and speaking skills for the IELTS examination.}
        \resumeItem{Provided one-to-one counselling to students with weak points in any section of the exam.}
        \resumeItem{Gave instructions and invigilated mock exams in classrooms of 40+ students.}
        \resumeItem{Conducted 3 seminars on applying abroad and securing funding, writing statement of purpose for graduate studies in the USA.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Standardized Tests-----------
\section{Standardized Tests}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Graduate Record Examination (GRE)} $|$ \emph{Overall: 317; AWA: 4.5}}{July 2023}
          \resumeItemListStart
            \resumeItem{Quant: 161 (65th Percentile); Verbal: 156 (70th Percentile)}
            \resumeItem{Analytical Writing: 4.5 (81st Percentile)}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{International English Language Testing System (IELTS)} $|$ \emph{Overall: 8.5}}{August 2023}
          \resumeItemListStart
            \resumeItem{Listening: 9; Reading: 9; Speaking: 8; Writing: 7.5}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Academic Courses}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Probability and Probability Distributions
                \item Linear Algebra
                \item Real Analysis
                \item Calculus 
                \item Test of Hypothesis
                \item Regression Analysis
                \item Multivariate Analysis
                \item Theory of Estimation
                \item Design and Analysis of Experiment
                \item Survival Analysis
                \item Stochastic

 Process
                \item Generalized Linear Models
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
        \vspace{-4pt}

    %\resumeSubHeadingListEnd
    


%-----------CLASSPROJECTS-----------
\section{Course Writing and Presentation}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Report Writing} $|$ \emph{\textbf{Course:} Industrial and Official Statistics}}{}
          \resumeItemListStart
            \resumeItem{Composed a report summarizing trends in \say{Infant Mortality in Bangladesh} based on the reports published by the Bangladesh Demographic and Health Survey (BDHS) program in the years 2017, 2014, 2011, and 2007.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Class Presentation} $|$ \emph{\textbf{Courses:} Sampling Techniques and Research Methodology}}{}
          \resumeItemListStart
            \resumeItem{Presented on the conceptual understanding of Stratified and Cluster sampling with illustrations and comparisons between the two sampling techniques.}
            \resumeItem{Presented on the introduction, purpose, and steps in the solution of a research topic as well as the stages of a research process based on the coursebook.}
          \resumeItemListEnd   
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
    \vspace{-5pt}
 \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Programming Language} $|$ \emph{R, Python, SQL}}{}
          \resumeItemListStart
          \resumeItem{Gained proficiency in Python and R for statistical exploration through MS course STAT-850: Statistical Computing.}
            \resumeItem{Leveraged statistical libraries in R such as \say{survival}, \say{tseries}, \say{qcc} to complete practical coursework for survival analysis, time series analysis, and industrial analysis.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Statistical Software and Scientific Writing} $|$ \emph{SPSS, SAS, Stata, Microsoft Excel, Rmarkdown, Quarto, Latex}}{}       
    \resumeSubHeadingListEnd
\vspace{-10pt}


%-----------INVOLVEMENT---------------
\section{Certification and Teaching Experience}
         \resumeItemListStart
                \resumeItem{\underline{Public Health}: Completed three Specialization programs on Coursera from Imperial College London, consisting of eleven total courses covering the foundations of Public Health, Epidemiology, and Statistical Analysis in R for Public Health as part of their Global MPH program.}
                \resumeItem{\underline{SAS}: Completed the SAS Programming Specialization on Coursera, that covered how to write syntax to access, transform, and analyze data, as a preparation for the SAS Base Programmer certification exam.}
                \resumeItem{\underline{SQL}: Learned SQL operations including basic querying, filtering, sorting, and joining data using PostgreSQL on the online learning platform Datacamp.}
                \resumeItem{\underline{R}: Gained proficiency in the tidyverse packages for exploratory data analysis and reproducibility tools like Rmarkdown/Quarto by completing over 30+ courses on Datacamp as part of their \say{Statistician and Data Scientist Career Track}.}
                \resumeItem{\underline{Teaching}: Tutored high school students in physics, chemistry, and math for eight months, helping them improve their understanding and grades in these subjects.}
         \resumeItemListEnd
         
%-----------AWARDS-----------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Othmer Fellowship Award}{August 2024}
      {Department of Statistics, University of Nebraska-Lincoln}{Lincoln, NE, USA}
        \resumeItemListStart
        \resumeItem{Awarded \$4,000 to assist with recruitment and support my studies at the University of Nebraska-Lincoln.}
      \resumeItemListEnd
      \resumeSubheading
      {General Scholarship}{2023}
      {University of Dhaka}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Received for outstanding academic performance during the Bachelor of Science in Statistics program.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
```
